Introduction

### 2023-05-22 episodes/introduction.Rmd
First part of MSA ready

Answer the quiz as you follow along, using this [link](https://pollev.com/lionelguy323/)
or by using the following QR code 
![QR code](fig/qr_code_quiz.png){alt='QR code linking to the interactive quiz'}

>>>>

Answer the quiz as you follow along, [using this link](https://pollev.com/lionelguy323/) or by using the following QR code ![QR code](fig/qr_code_quiz.png){alt='QR code linking to the interactive quiz'}
